---
title: "Checking out packages `apaTables` & `stargazer`"
author: "Jürgen Schneider"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
# library(fontawesome)
# `r fa("git-alt")`
```

\
\


# apaTables

Check out the vignette on [github pages](https://dstanley4.github.io/apaTables/articles/apaTables.html).

\
\

## load package(s)

```{r}
library(apaTables)

# I don't get out of bed without...
library(tidyverse)
library(skimr)
```

\
\


## check out integrated data set {.tabset}

### via `glimpse`

You can use `glimpse` to get a glimpse (obviously)
```{r, eval=FALSE}
library(tidyverse)
glimpse(attitude)
```

### via `skimr`

Or `skim` to get descriptives

```{r, eval=FALSE}
library(skimr)
skim(attitude)
```



\
\



## Correlation

This package is illegally simple to use. The downside: There are close to none setting options.   
  
Functions always need three arguments:

```{r, results='hide'}
apa.cor.table(attitude,  # provide the data set / fit objects
              filename="exported_tables/Table1_APA1.doc", # where should the doc be saved?
              table.number=1   # which number should the table have?
              )
```

\
\


## Regression tables 1 {.tabset}

### Task

1. check out the data set `album` that comes with the package
2. make 2 regressions:
   + regress `sales`on `adverts` and `airplay` without interaction
   + regress `sales`on `adverts` and `airplay` with interaction
3. plot both results in one table with `apa.reg.table()`


### I need help with the regressions

Have you tried these things?

* The function for regressions is `lm()`
* `lm()` need two arguments: a formula and the data
   + the data is `album`
   + the formula has the form `DV ~ predictor1 + predictor2 + ...`
   + to specify an interaction you'll simply need to multiply the two predictors and add this to the formula (`... + (predictor1 * predictor2)`)
   
   
### I need help with `apa.reg.table()`

* check out the help via `?apa.reg.table`
* check out the [vignette under "blocks regression table"](https://dstanley4.github.io/apaTables/articles/apaTables.html)

### Solution


```{r, results='hide'}
glimpse(album)

# Regression 1
block1 <- lm(sales ~ adverts + airplay, 
             data = album)

# Regression 2
block2 <- lm(sales ~ adverts + airplay + (adverts*airplay), 
             data = album)

# Create table
apa.reg.table(block1, block2, 
              filename = "exported_tables/Table3_APA.doc", 
              table.number = 3)
```


\
\

## Regression tables 2

After you checked out `stargazer`:  
Try out the package with your own data?


\
\




# stargazer

Check out the [cheat sheet](https://www.jakeruss.com/cheatsheets/stargazer).  
  
When using stargazer in RMarkdown you'll need to

1. use the argument `type = "html"`
2. set chunk options to `{r, results='asis'}`

When using stargazer in RStudio (console output) you'll need to

1. use the argument `type = "text"`


```{r, results='asis'}
library(stargazer)

stargazer(album, type = "html")
```

\
\

Then you'd need to copy and paste the Table to Word.

\
\


## Regression table {.tabset}

### task

1. Use the two regression fit objects you created before and use them in `stargazer`!
2. Tweak the table to your liking. You could for example...
   + display t and p-values instead of SE (with the `report` argument -> check the help!)
   + change the variable labels (check out the [description in the vignette](https://www.jakeruss.com/cheatsheets/stargazer/#labelling-the-table))
   
### Solution 1

```{r, eval=FALSE}
stargazer(block1, block2, type = "text")
```

```{r, echo=FALSE, results='asis'}
stargazer(block1, block2, type = "html")
```

### Solution 2a

```{r, eval=FALSE}
stargazer(block1, block2, 
          type = "text", 
          title            = "These are awesome results!",
          covariate.labels = c("Evil Adverts", "Strong Winds", "Interaction(Adverts*Winds)"),
          dep.var.caption  = "Effects on..",
          dep.var.labels   = "Feeding time of 1 Gummibärchenpackung")
```

```{r, echo=FALSE, results='asis'}
stargazer(block1, block2, 
          type = "html", 
          title            = "These are awesome results!",
          covariate.labels = c("Evil Adverts", "Strong Winds", "Interaction(Adverts*Winds)"),
          dep.var.caption  = "Effects on..",
          dep.var.labels   = "Feeding time of 1 Gummibärchenpackung")
```

### Solution 2b


```{r, eval=FALSE}
stargazer(block1, block2, 
          type = "text", 
          report = "vctp")
```

```{r, echo=FALSE, results='asis'}
stargazer(block1, block2, 
          type = "html", 
          report = "vctp")
```