---
title: "Hello there, ~~General~~ R"
subtitle: ""
author: 
  - Jürgen Schneider
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  ioslides_presentation:
    widescreen: true
    smaller: true
    logo: ../www/logo.gif
    css:  ../www/style.css
bibliography: ../www/references.bib
editor_options: 
  chunk_output_type: console
---

<style>
slides > slide:not(.nobackground):after {
  content: '';
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# download.file("https://drive.google.com/uc?export=download&id=1wuMqL_Z8T9rxuGvn0VP6siag90kHDm2O", 
#               "../www/references.bib", overwrite = T)

```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

