---
title: "Whipping up some plots with `ggplot2`"
author: "Jürgen Schneider"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Where can I find these scripts?

It's on github: https://github.com/j-5chneider/howR  
  
If you want to pull the project, use:

1. Menu "file" > "New Project" > "Version Control" > "Git"  
2. put `https://github.com/j-5chneider/howR.git` in the field "Repository URL" and select a location where RStudio should save the new project folder
3. Click "Create Project" and let RStudio pull the entire folder on your local drive

When you want to pull the newest updates I made to the github repository, go to the `git` tab in RStudio and click "pull".

# Today's data set

We'll check out our data set using two options to get a quick overview:

```{r , warning=F, message=F}
library(tidyverse)
glimpse(iris)

library(skimr)
skim(iris)
```


# `geom_point()`

```{r}
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width)) +
  geom_point()
```

## Themes make it way nicer

with very little effort

```{r}
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width)) +
  geom_point() +
  theme_light()
```

# `geom_jitter()`

Sometimes it makes sense to spread the data a little bit, so that points points that lay on the same coordinates are not stacked upon each other.  
Disadvantage: The points are not plotted exactly on the coordinates where they should be located. This means, that the points are visually biased.  
  
Compare this result with `geom_point()`!

```{r}
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width)) +
  geom_jitter() +
  theme_light()

```

## unbiased with factor

In case you'll use a categorical variable, the jitter doesn't bias the view.

```{r}
ggplot(iris, aes(x=Species, y=Sepal.Width)) +
  geom_jitter() +
  theme_light()
```

In this case jitter is very usesfull. Compare this result with using `geom_point()`!

```{r}
ggplot(iris, aes(x=Species, y=Sepal.Width)) +
  geom_point() +
  theme_light()

```

# `geom_boxplot()`

Let's add a boxplot over the points. We added `geom_boxplot()` after `geom_jitter()`, therefore it will lay above the points.  

## with `alpha`
  
The argument `alpha=0.5` enables us to make the boxplot 50% transparent, so that we see the points below.

```{r}
ggplot(iris, aes(x=Species, y=Sepal.Width)) +
  geom_jitter() +
  geom_boxplot(alpha=0.5) +
  theme_light()

```


## nudged in its position

We can also push the boxplot aside a bit so that it doesn't overlay the points.  
  
Also, we can limit the width of the jitter.

```{r}
ggplot(iris, aes(x=Species, y=Sepal.Width)) +
  geom_jitter(width = .1) +
  geom_boxplot(alpha=0.5, 
               position = position_nudge(x=-.2),
               width=.1) +
  theme_light()
```

# `geom_violin()`

In my poinion they show the distribution of data very good (e.g. compared to boxplots).

```{r}
ggplot(iris, aes(x=Species, y=Sepal.Width)) +
  geom_jitter(width = .1) +
  geom_boxplot(alpha=0.5, 
               position = position_nudge(x=-.2),
               width=.1) +
  geom_violin(position = position_nudge(x=.2),
              width=.1) +
  theme_light()
```


# `geom_smooth()`

If you want to plot a regression line you can use `geom_smooth()`


```{r}
ggplot(iris, aes(x=Sepal.Width, y=Sepal.Length)) +
  geom_jitter() +
  geom_smooth(method="lm") +
  theme_light()
```

## One line per group

In case you are doing "multilevel stuff", you can plot one regression line for each group.  
You can either specify this within an aesthetics function in `geom_smooth()`...

```{r}
ggplot(iris, aes(x=Sepal.Width, y=Sepal.Length)) +
  geom_jitter() +
  geom_smooth(aes(color=Species), method="lm") +
  theme_light()
```

... or define it in the aesthetics function at the beginning, in the `ggplot()` function.  
See the difference? If you define it in the `ggplot()` function, the coloring will be applied to all geoms (jitter and smooth).

```{r}
ggplot(iris, aes(x=Sepal.Width, y=Sepal.Length, color=Species)) +
  geom_jitter() +
  geom_smooth(method="lm") +
  theme_light()
```

### Print-friendly (grayscale friendly)

We can also differentiate the groups by using different linetypes. Most journals only take grayscal-friendly plots.

```{r}
ggplot(iris, aes(x=Sepal.Width, y=Sepal.Length, linetype=Species)) +
  geom_jitter() +
  geom_smooth(method="lm") +
  theme_light()
```

To actually make it grayscale, we need to define the blue lines as black.  
But wait. Doesn't this simply differentiate between groups like above (`color=Species`)?  
No. Only if you put `color = ...` in the `aes()` function and feed it a variable to differentiate the groups.  
In this case (below), we simply tell the `geom_smooth()` function to set the color to black.


```{r}
ggplot(iris, aes(x=Sepal.Width, y=Sepal.Length, linetype=Species)) +
  geom_jitter() +
  geom_smooth(method="lm", color = "black") +
  theme_light()
```


OF course we can also combine two groupings (linetype and color).

```{r}
ggplot(iris, aes(x=Sepal.Width, y=Sepal.Length, linetype=Species, color = Species)) +
  geom_jitter() +
  geom_smooth(method="lm") +
  theme_light()
```

### Artifically creating groups

In this case we want to compare 

* subjects that lay at least one SD above the mean with
* subjects that lay at least one SD below the mean with
* subjects that lay "around the mean" (plus/minus one SD)

```{r}
interaction_sd <- iris |>
  # let's create a grouping variable with these 3 groups
  mutate(mod_groups = case_when(
                          Sepal.Length < mean(Sepal.Length) - sd(Sepal.Length) ~ -1, # group -1 SD
                          Sepal.Length > mean(Sepal.Length) + sd(Sepal.Length) ~ 1,  # group +1 SD
                          TRUE ~ 0                                                   # the rest
  ))


ggplot(interaction_sd, aes(Petal.Width, Petal.Length, linetype = as.factor(mod_groups))) +
  geom_jitter() +
  geom_smooth(method="lm") +
  theme_light()
```

