---
title: "How to Quarto Book"
subtitle: ""
author:
  - name: "Jürgen Schneider"
    email: "ju.schneider@dipf.de"
    affiliation: "DIPF"
    correspondence: true
date: "`r Sys.Date()`" # inserts the date of compiling
editor: source
execute:
  eval: false
  echo: true
  warning: false
  message: false
  cache: false # true will prevent embed-resources
format: 
  html:
    theme: ceruleanc
    number-sections: true
    fontsize: 0.85em
    toc: true
    toc-location: left
    toc-depth: 3
    embed-resources: true # will make standalone html file
    # code-fold: show
    # code-tools: true
    code-link: true
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false
#| eval: true

library(fontawesome)
```

# Create new project > "Quarto book"
- check "use renv with this project"
- check "create a git repository"

# Create pages
Put file names in `_quarto.yml`

# Put this into .gitignore
/.quarto/  
/_site/


# Publish

## Let Git know who you are

::: {.panel-tabset}

### Via `usethis`
First time, connect to github:
renv::install("usethis")

```{r}
usethis::use_git_config(
  user.name = "Jane Doe", # <-- change to your name
  user.email = "jane@example.org", # <-- and your email
  init.defaultBranch = "main") # <-- not necessary but kinder than 'master'
```

### Alternative via terminal

Click on the `Terminal` tab (right next to the `Console` tab).  
Give your user name and email.

```
git config user.name "Mona Lisa"
git config user.email "mona@lisa.org"
```

:::

## Initiate Git

```{r}
usethis::use_git()
```


## Connect to GitHub
Create GitHub Token and copy it.

```{r}
usethis::create_github_token(description = "Token for project ...") # <-- Fill in a name of your token
```

And now set the PAT, to identify yourself.
```{r}
credentials::set_github_pat() # <-- Token must *not* go into brackets, paste when asked in popup
```

## Create GitHub repo

```{r}
usethis::use_github()
```



## Publish as GitHub Pages

Put this into the **terminal**:

```{r}
quarto publish gh-pages
```