---
title: "Quarto"
subtitle: "Options and Basic Intro"
author:
  - name: "Jürgen Schneider"
    email: "ju.schneider@dipf.de"
    affiliation: "DIPF"
    correspondence: true
  - name: "Exemplary Coauthor"
    affiliation: "Other Institute"
date: "`r Sys.Date()`" # inserts the date of compiling
editor: source
execute:
  echo: true
  warning: false
  message: false
  cache: false # true will prevent embed-resources
format: 
  html:
    theme: solar
    fontsize: 0.85em
    toc: true
    toc-location: left
    toc-depth: 4
    embed-resources: true # will make standalone html file
    code-fold: show
    code-tools: true
    code-link: true
bibliography: ../www/references.bib
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/apa.csl
---

# Session Info

Always provide your R-Version and libraries when producing reproducible reports.

```{r}
library(here)
library(xfun)
library(palmerpenguins)

sessionInfo()
```


# Options & Layout

::: callout-tip
## Basic intro to Quarto

<https://quarto.org/docs/get-started/hello/rstudio.html>
:::

## YAML

```{yaml}
#| eval: false
---
title: "Test"
author:
  - name: "Jürgen Schneider"
    email: "ju.schneider@dipf.de"
    affiliation: "DIPF"
    correspondence: true
  - name: "First Coauthor"
    affiliation: "other institute"
date: last-modified # other option is: today
date-format: "DD MMMM YYYY"
editor: source
execute:
  echo: true
  warning: false
  message: false
  cache: false # true will prevent embed-resources
format: 
  html:
    theme: solar
    fontsize: 0.85em
    toc: true
    toc-location: left
    toc-depth: 4
    embed-resources: true # will make standalone html file
    code-fold: show
    code-tools: true
    code-link: true
bibliography: ../www/references.bib
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/apa.csl
---
```

## Themes

Check out different themes:

<https://quarto.org/docs/output-formats/html-themes.html>

and put the name as argument in:

```{yaml}
#| eval: false

format: 
  html:
    theme: solar
```

## Standalone HTML

::: panel-tabset
### Option 1

In the **YAML** set `embed-resources: true`

```{yaml}
#| eval: false

format: 
  html:
    embed-resources: true 
```

**and don't** set `cache: true`. So, cache must be false:

```{yaml}
#| eval: false

execute:
  cache: false
```

### Option 2

If you need to set `cache: true`, you might be able to embed resources by adding an additional r cell (chunk) with this content:

```{r}
#| eval: false

# This will (sometimes...) prevent embed-resources to be prevented when cache: true
knitr::opts_chunk$set(fig.path = knitr::opts_chunk$get('cache.path'))
```

This works sometimes, but not always - in my experience.

### Check and troubleshoot

-   While rendering the file, quarto generates a "...\_files" folder in the files-pane of RStudio. This folder should disappear after rendering is done. If it doesn't disappear, the html file probably isn't standalone.
-   If you think you have set all options correct for the file to be standalone and it still doesn't work:
    -   Create a new quarto file with a new name
    -   copy the code from the old file and paste it to the new file
    -   try rendering the new file
:::

# Running R Code

::: callout-tip
## Computations in Quarto

<https://quarto.org/docs/get-started/computations/rstudio.html>
:::

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
plot(iris$Sepal.Length, iris$Sepal.Width)
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

# Other (cool) stuff

::: callout-tip
## Basic intro to Quarto

<https://quarto.org/docs/get-started/authoring/rstudio.html>
:::

## Embed any file in the HTML

Use the `xfun` package to embed any file into the html. Users can click and download the file from there without internet connection.

Click here to download the `r xfun::embed_file(here('www/never.gif'), text = "qualitative data")` on the topic of never giving up.

Here I used the function `embed_file()`:

```{r}
#| eval: false
`r xfun::embed_file(here("www/never.gif"), text = "qualitative data")`
```

The function `here()` will always start searching for the file from the working directory. This is important, if you move the qmd-file to other folders.

## Tabsets

Wrap `::: {.panel-tabset}` and `:::` around headings. For example:

```{quarto}
#| eval: false

::: {.panel-tabset}

## This is tab 1
This is text within the tab.

## This is tab 2
plot(penguins$bill_length_mm, penguins$bill_depth_mm)

:::

```


## References

1. Export your references to a BibTex-file (.bib file ending)
2. Specify the location of the file in the YAML header of your Quarto document.
```{yaml}
#| eval: false

---
title: 'This is my cool Quarto document' 
bibliography: ../www/references.bib
---
```

3. If you want, provide a citation style (via `.csl` file). This URL sets the style to APA 7.

```{yaml}
#| eval: false

---
title: 'This is my cool Quarto document' 
bibliography: ../www/references.bib
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/apa.csl
---
```

4. Cite in the body of your text by using "[@...]". E. g. [\@mayer.2014] will give [@mayer.2014]. A list of references will be automatically produced at the end of the document.
